Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-16 lqg-strings.tex
minor addition to ddiscussion section
added a paragraph relating the Delta field to Kalb-Rammond field

One could also consider a more general form of action \eqref{eqn:emergent-dimensions-action} by swapping the flat Minkowski metric $\eta _{\mu \nu}$ by a more general curved metric $G_{\mu \nu}$ and considering off-diagonal mass parameters $m_{\mu \nu}$:
\begin{multline} \label{eqn:emergent-dimensions-curved}
	S' _{E D} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} + \\
	+ \mu _{0} ^2 \e ^{- m_{\mu \nu} / T} X^{\mu} X^{\nu} G_{\mu \nu} \big) ,
\end{multline}
where the mass parameters will be constrained as in
\begin{equation} \label{eqn:X-masses-constraint-2}
	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n \alpha}}{T} \frac{p_{\alpha} ^n}{E_{pl} ^n} ,
\end{equation}
since those are the ones that show up in the $X^{\mu}$ equations of motion
\begin{multline}
	g^{a b} \nabla _{a} \nabla _{b} X^{\mu} G_{\mu \lambda} - \mu _{0} ^2 \e ^{- m_{\mu \lambda} / T} X^{\mu} G_{\mu \lambda} = \\
	= \frac{1}{2} g^{a b} \del_{a} X^{\mu} \del _{b} X^{\nu} \del _{\lambda} G_{\mu \nu} .
\end{multline}

@@

Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor:
\begin{equation} \label{eqn:variation-wrt-g}
	\frac{\delta S_{P B}}{\delta g^{c d}} = 0
\end{equation}
\begin{multline} \label{eqn:g-em-tensor}
	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}} ,
\end{multline}
and completely analogous for the $H_{\mu \nu}$ metric,
\begin{equation} \label{eqn:variation-wrt-h}
	\frac{\delta S_{P B}}{\delta h^{c d}} = 0
\end{equation}
\begin{multline} \label{eqn:h-em-tensor}
	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
\end{multline}
If we assume no interaction term $S_{int} = 0$, we get the expected expressions for the auxiliary metrics $g_{c d}$ and $h_{c d}$ as in
\begin{equation} \label{eqn:g-expression}
	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f^{(G)}$ is given by
\begin{equation} \label{eqn:g's-f-function}
	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
\end{equation}
and for $h_{c d}$
\begin{equation} \label{eqn:h-expression}
	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
\end{equation}
with $f^{(H)}$ given by
\begin{equation} \label{eqn:h's-f-function}
	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
\end{equation}
If the auxiliary metrics $g_{c d}$ and $h_{c d}$ coincide with the pullback metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, the action with no interaction reduces to
\begin{equation} \label{eqn:double-NG-action}
	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
\end{equation}
and from here we note that if $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-NG-action}
\begin{equation} \label{eqn:area-corrected-NG-from-bimetric}
	S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
\end{equation}
The condition $h = \Delta ^2 / g$ can be achieved by
\begin{equation} \label{eqn:h=SgS}
	h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d} .
\end{equation}
This implies that
\begin{multline} \label{eqn:SgS-implication}
	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \widetilde{\varepsilon} ^{c c'} \Delta _{b d} \widetilde{\varepsilon} ^{d d'} G_{\mu \nu} \right) \times \\
	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0 ,
\end{multline}
which can be achieved if
\begin{equation} \label{eqn:S=sigma_y}
	\Delta _{a c} = \sqrt{\Delta} \widetilde{\varepsilon} _{a c}
\end{equation}
and if the background metrics are related by
\begin{equation} \label{eqn:H=1/(2g)G}
	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} ,
\end{equation}
which makes sense since $\Delta _{a b}$ is related to area, so it should be a 2-form.

>>>>

One could also consider a more general form of action \eqref{eqn:emergent-dimensions-action} by swapping the flat Minkowski metric $\eta _{\mu \nu}$ by a more general curved metric $G_{\mu \nu}$ and considering off-diagonal mass parameters $m_{\mu \nu}$:
\begin{multline} \label{eqn:emergent-dimensions-curved}
	S' _{E D} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} + \\
	+ \mu _{0} ^2 \e ^{- m_{\mu \nu} / T} X^{\mu} X^{\nu} G_{\mu \nu} \big) ,
\end{multline}
where the mass parameters will be constrained as in
\begin{equation} \label{eqn:X-masses-constraint-2}
	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n \alpha}}{T} \frac{p_{\alpha} ^n}{E_{pl} ^n} ,
\end{equation}
since those are the ones that show up in the $X^{\mu}$ equations of motion
\begin{multline}
	g^{a b} \nabla _{a} \nabla _{b} X^{\mu} G_{\mu \lambda} - \mu _{0} ^2 \e ^{- m_{\mu \lambda} / T} X^{\mu} G_{\mu \lambda} = \\
	= \frac{1}{2} g^{a b} \del_{a} X^{\mu} \del _{b} X^{\nu} \del _{\lambda} G_{\mu \nu} ,
\end{multline}
where $\nabla _{a}$ denotes the 2-dimensional covariant derivative with respect to the Levi-Civita connection $\Gamma _{a b} ^{c}$.

@@

Following the usual procedure such as the one found in \cite{Tong2009Lectures}, we find two copies of the string energy-momentum tensor:
\begin{equation} \label{eqn:variation-wrt-g}
	\frac{\delta S_{P B}}{\delta g^{c d}} = 0
\end{equation}
\begin{multline} \label{eqn:g-em-tensor}
	T^{(G)} _{c d} := G_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\nu} - \\
	- \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T} \frac{\delta S_{int}}{\delta g^{c d}} ,
\end{multline}
and completely analogous for the $H_{\mu \nu}$ metric,
\begin{equation} \label{eqn:variation-wrt-h}
	\frac{\delta S_{P B}}{\delta h^{c d}} = 0
\end{equation}
\begin{multline} \label{eqn:h-em-tensor}
	T^{(H)} _{c d} := H_{\mu \nu} \bigg( \partial _{c} X^{\mu} \partial _{d} X^{\mu} - \\
	- \frac{1}{2} h_{c d} h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \bigg) = \frac{2}{T'} \frac{\delta S_{int}}{\delta h^{c d}} .
\end{multline}
If we assume no interaction term $S_{int} = 0$, we get the expected expressions for the auxiliary metrics $g_{c d}$ and $h_{c d}$ as in
\begin{equation} \label{eqn:g-expression}
	g_{c d} = 2 f^{(G)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f^{(G)}$ is given by
\begin{equation} \label{eqn:g's-f-function}
	\frac{1}{f^{(G)}} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu}
\end{equation}
and for $h_{c d}$
\begin{equation} \label{eqn:h-expression}
	h_{c d} = 2 f^{(H)} \partial _{c} X^{\mu} \partial _{d} X^{\nu} H_{\mu \nu} ,
\end{equation}
with $f^{(H)}$ given by
\begin{equation} \label{eqn:h's-f-function}
	\frac{1}{f^{(H)}} = h^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} H_{\mu \nu} .
\end{equation}
If the auxiliary metrics $g_{c d}$ and $h_{c d}$ coincide with the pullback metrics from $G_{\mu \nu}$ and $H_{\mu \nu}$, the action with no interaction reduces to
\begin{equation} \label{eqn:double-NG-action}
	S = - T \int \diff ^2 x \sqrt{- g} - T' \int \diff ^2 x \sqrt{- h} ,
\end{equation}
and from here we note that if $T' = - T k / 2$ and $h = \Delta ^2 / g$, we recover the Nambu-Goto area-corrected action \eqref{eqn:modified-NG-action}
\begin{equation} \label{eqn:area-corrected-NG-from-bimetric}
	S = - T \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) .
\end{equation}
The condition $h = \Delta ^2 / g$ can be achieved by
\begin{equation} \label{eqn:h=SgS}
	h_{a b} = \Delta _{a c} \Delta _{b d} g^{c d} .
\end{equation}
This implies that
\begin{multline} \label{eqn:SgS-implication}
	\left( \delta _{a} ^{c'} \delta _{b} ^{d'} H_{\mu \nu} - \frac{1}{2 g} \Delta _{a c} \widetilde{\varepsilon} ^{c c'} \Delta _{b d} \widetilde{\varepsilon} ^{d d'} G_{\mu \nu} \right) \times \\
	\times \del _{c'} X^{\mu} \del _{d'} X^{\nu} = 0 ,
\end{multline}
which can be achieved if
\begin{equation} \label{eqn:S=sigma_y}
	\Delta _{a c} = \sqrt{\Delta} \widetilde{\varepsilon} _{a c}
\end{equation}
and if the background metrics are related by
\begin{equation} \label{eqn:H=1/(2g)G}
	H_{\mu \nu} = \frac{\Delta}{2 g} G_{\mu \nu} ,
\end{equation}
which makes sense since $\Delta _{a b}$ is related to area, so it should be a 2-form. Since $g_{a b}$ is taken to be the pullback of the background metric $G_{\mu \nu}$, $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$, which is a part of the spin-2 spectrum of the closed string, perhaps the quantum area correction field $\Delta _{a b}$ is related to the pullback of the background Kalb-Rammond 2-form, which is the other half of the first excitation of the closed spin-2 spectrum,
\begin{equation} \label{eqn:Delta-B-relation}
	\Delta _{a b} \sim \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} ,
\end{equation}
thus giving a concrete physical interpretation for the $B_{\mu \nu}$ field as being related directly to quantum geometry.
